### 2009-10-30 doc/manuals/user_interface/ui-brokers.tex
Some clean-up in bibliography and layout

Possible broker values for the \texttt{arcsub} command line option \verb#-b# are:
\begin{itemize}
 \item[--] \texttt{Random} -- ranks targets randomly (default)
 \item[--] \texttt{FastestQueue} -- ranks targets according to their queue length
 \item[--] \texttt{Benchmark[:name]} -- ranks targets according to a given benchmark, as specified by the \texttt{name}. If no benchmark is specified, CINT2000~\footnote{http://www.spec.org/cpu2000/CINT2000/} is used
 \item[--] \texttt{Data} -- ranks targets according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
 \item[--] \texttt{Python:$<$module$>$.$<$class$>$[:arguments]} -- ranks targets using any user-supplied custom Python broker module, optionally with broker arguments. Such module can reside anywhere in user's \texttt{PYTHONPATH}
 \item[--] \texttt{$<$otherbroker$>$[:arguments]} -- ranks targets using any user-supplied custom C++ broker plugin, optionally with broker arguments. Default location for broker plugins is \texttt{/usr/lib/arc} (may depend on the operating system), or the one specified by the \texttt{ARC\_PLUGIN\_PATH}.
\end{itemize}

To write a custom broker in C++ one has to write a new specialization of the \texttt{Broker} base class and implement the \texttt{SortTargets} method in the new class. The class should be compiled as a loadable
module that has the proper ARC plugin descriptor for the new broker. For example, to build a broker plugin ``MyBroker'' one executes:
\begin{lstlisting}
  g++ -I /arc-install/include \
      -L /arc-install/lib \
      `pkg-config --cflags glibmm-2.4 libxml-2.0` \
      -o libaccmybroker.so -shared MyBroker.cpp
\end{lstlisting}
For more details, refer to \textit{libarclib} documentation~\ref{cite:libarcclient}.

>>>>

Possible \index{broker}broker values for the \texttt{arcsub} command line option \verb#-b# are:
\begin{itemize}
 \item[--] \texttt{Random} -- ranks targets randomly (default)
 \item[--] \texttt{FastestQueue} -- ranks targets according to their queue length
 \item[--] \texttt{Benchmark[:name]} -- ranks targets according to a given benchmark, as specified by the \texttt{name}. If no benchmark is specified, CINT2000~\footnote{http://www.spec.org/cpu2000/CINT2000/} is used
 \item[--] \texttt{Data} -- ranks targets according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
 \item[--] \texttt{Python:$<$module$>$.$<$class$>$[:arguments]} -- ranks targets using any user-supplied custom Python broker module, optionally with broker arguments. Such module can reside anywhere in user's \texttt{PYTHONPATH}
 \item[--] \texttt{$<$otherbroker$>$[:arguments]} -- ranks targets using any user-supplied custom C++ broker plugin, optionally with broker arguments. Default location for broker plugins is \texttt{/usr/lib/arc} (may depend on the operating system), or the one specified by the \texttt{ARC\_PLUGIN\_PATH}.
\end{itemize}

To write a custom broker in C++ one has to write a new specialization of the \texttt{Broker} base class and implement the \texttt{SortTargets} method in the new class. The class should be compiled as a loadable
module that has the proper ARC plugin descriptor for the new broker. For example, to build a broker plugin ``MyBroker'' one executes:
\begin{lstlisting}[language=sh]
  g++ -I /arc-install/include \
      -L /arc-install/lib \
      `pkg-config --cflags glibmm-2.4 libxml-2.0` \
      -o libaccmybroker.so -shared MyBroker.cpp
\end{lstlisting}
For more details, refer to \textit{libarclib} documentation~\cite{libarcclient}.

### 2009-10-30 doc/manuals/user_interface/ui-job.tex
Some clean-up in bibliography and layout

Since  the  information  about  a job retrieved from a clsuter can be slightly out of date if the user very recently
submitted or removed a job, a warning is issued when this command is run. The \verb#--force# option disables this warning.

%If a specific cluster is selected for the syncronisation while the job list contains jobs  on  a  different  cluster,
%running  the arcsync command will remove the old jobs from the joblist, unless the \verb#--merge# option is given, in which
%case the new found jobs are merged with the jobs already in the joblist.

@@

\begin{framed}
\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<JobDefinition
 xmlns="http://schemas.ggf.org/jsdl/2005/11/jsdl"
 xmlns:posix="http://schemas.ggf.org/jsdl/2005/11/jsdl-posix">
 <JobDescription>
   <JobIdentification>
     <JobName>Hello World job</JobName>
   </JobIdentification>
   <Application>
     <posix:POSIXApplication>
       <posix:Executable>/bin/echo</posix:Executable>
       <posix:Argument>'Hello World'</posix:Argument>
       <posix:Output>out.txt</posix:Output>
       <posix:Error>err.txt</posix:Error>
     </posix:POSIXApplication>
   </Application>
   <DataStaging>
     <FileName>out.txt</FileName>
     <CreationFlag>overwrite</CreationFlag>
     <DeleteOnTermination>false</DeleteOnTermination>
   </DataStaging>
   <DataStaging>
     <FileName>err.txt</FileName>
     <CreationFlag>overwrite</CreationFlag>
     <DeleteOnTermination>false</DeleteOnTermination>
   </DataStaging>
 </JobDescription>
</JobDefinition>
\end{verbatim}
\end{framed}

>>>>

Since  the  information  about  a job retrieved from a cluster can be slightly out of date if the user very recently
submitted or removed a job, a warning is issued when this command is run. The \verb#--force# option disables this warning.

If the job list is not empty when invoking syncronisation, the old jobs will be merged with the new jobs, unless the \verb#--truncate# option is given, in which case the job list will first be truncated and then the new jobs will be added.

@@

\begin{lstlisting}[language=xml]
<?xml version="1.0" encoding="UTF-8"?>
<JobDefinition
 xmlns="http://schemas.ggf.org/jsdl/2005/11/jsdl"
 xmlns:posix="http://schemas.ggf.org/jsdl/2005/11/jsdl-posix">
 <JobDescription>
   <JobIdentification>
     <JobName>Hello World job</JobName>
   </JobIdentification>
   <Application>
     <posix:POSIXApplication>
       <posix:Executable>/bin/echo</posix:Executable>
       <posix:Argument>'Hello World'</posix:Argument>
       <posix:Output>out.txt</posix:Output>
       <posix:Error>err.txt</posix:Error>
     </posix:POSIXApplication>
   </Application>
   <DataStaging>
     <FileName>out.txt</FileName>
     <CreationFlag>overwrite</CreationFlag>
     <DeleteOnTermination>false</DeleteOnTermination>
   </DataStaging>
   <DataStaging>
     <FileName>err.txt</FileName>
     <CreationFlag>overwrite</CreationFlag>
     <DeleteOnTermination>false</DeleteOnTermination>
   </DataStaging>
 </JobDescription>
</JobDefinition>
\end{lstlisting}

### 2009-10-30 doc/manuals/user_interface/ui.tex
Added Proxy and Configuration sections
CLI manual: moved chelonia section under doc/chelonia, fixed Makefile
Added brokers description as a separate file, other small fixes
Some clean-up in bibliography and layout

\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}[1]{\colorbox{shadecolor}{\texttt #1}}
\newcommand{\xrsl}[1]{\textbf{\sffamily #1}}
\newcommand{\uicommand}[1]{\textbf{\sffamily #1}}
\newcommand{\versions}[1]{\vspace{-0.3cm}(#1)\par}
\newcommand{\GT}{Globus Toolkit$\mathrm{^{TM}}$}
\newcommand{\globus}{Globus\textsuperscript{\textregistered}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{cyan}{rgb}{0,1,1}

@@

@@

@@

\bibliography{grid}
\printindex

>>>>

\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}[1]{\colorbox{shadecolor}{\texttt #1}}
\newcommand{\xrsl}[1]{\textbf{\sffamily #1}}
\newcommand{\uicommand}[1]{\textbf{\sffamily #1}}
\newcommand{\versions}[1]{\vspace{-0.3cm}(#1)\par}
\newcommand{\GT}{Globus Toolkit$\mathrm{^{TM}}$}
\newcommand{\globus}{Globus\textsuperscript{\textregistered}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{cyan}{rgb}{0,1,1}
\definecolor{grey}{rgb}{0.9,0.9,0.9}

\usepackage{listings}
 \lstset{
         basicstyle=\small\ttfamily,
         numbers=none,
         numberstyle=\tiny,
         stepnumber=1,
         numbersep=5pt,
         tabsize=2,
         extendedchars=true,
         breaklines=true,
         keywordstyle=\color{red},
                frame=b,         
 %        keywordstyle=[1]\textbf,
 %        keywordstyle=[2]\textbf,
 %        keywordstyle=[3]\textbf,
 %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %
         stringstyle=\color{blue}\ttfamily,
         showspaces=false,
         showtabs=false,
         xleftmargin=17pt,
         frame=single,
         framexleftmargin=17pt,
         framexrightmargin=5pt,
         framexbottommargin=4pt,
         framextopmargin=4pt,
         backgroundcolor=\color{grey},
         showstringspaces=false     
 }
 \lstloadlanguages{
         sh,
         bash,
         Python,
         PHP,
         Perl,
         C,
         C++,
         XML,
         HTML,
         Java
 }

@@

\section{Proxy utilities} \label{sec:proxy}
\index{security} ARC now comes complete with a set of utilities to create
temporary user credentials (proxies) used to access Grid services.

\input{ui-proxy}

@@

\input{chelonia-cli}

@@

\bibliography{grid,nordugrid}
\printindex
